Analyzing DECREASE trials for extent of data fabrication

### 2016-04-29 submission/manuscript.Rmd
Add confidence interval plots

load('../data/result_almost_iv_uncertain')
load('../data/result_almost_iv_certain')
# 
# load('data/result_almost_i_uncertain')
# load('data/result_almost_i_certain')
# 
# load('data/result_almost_iv_uncertain')
# load('data/result_almost_iv_certain')

res_i_uncertain <- apply(result_almost_i_uncertain, 2, sum) / iterations
res_i_certain <- apply(result_almost_i_certain, 2, sum) / iterations

par(mar = c(2.5, 5, 0.5, 0.5),
    mfrow = c(2, 1))
plot(res_i_uncertain,
     xlab = '',
     ylab = 'Proportion',
     ylim = 0:1,
     type = 'l',
     lty = 1)
lines(res_i_certain, pch = 2, type = 'l', lty = 2)
abline(h = c(.025, .975), lty = 3)

legend(x = 0, y = .5, bty = 'n', lty = c(1, 2), legend = c("Distribution estimate", "Point estimate"))

clip(x1 = 0, x2 = length(res_i_uncertain), y1 = 0.025, y2 = .975)
abline(v = which(abs(res_i_uncertain - .975) == min(abs(res_i_uncertain - .975))), lty = 1)
abline(v = which(abs(res_i_certain - .975) == min(abs(res_i_certain - .975))), lty = 2)

res_iv_uncertain <- apply(result_almost_iv_uncertain, 2, sum) / iterations
res_iv_certain <- apply(result_almost_iv_certain, 2, sum) / iterations

@@

legend(x = 0, y = .55, bty = 'n', lty = c(1, 2), legend = c("Distribution estimate", "Point estimate"))

clip(x1 = 0, x2 = length(res_iv_uncertain), y1 = 0.025, y2 = .975)
abline(v = which(abs(res_iv_uncertain - .975) == min(abs(res_iv_uncertain - .975))), lty = 1)
abline(v = which(abs(res_iv_certain - .975) == min(abs(res_iv_certain - .975))), lty = 2)
```

|            | Estimate              | Lowerbound  | Upperbound | N    |
|-------------|-----------------------|-------------|------------|------|
| DECREASE-I  | Distribution estimate | 0           | 79;85;90   | 113  |
|            | Point estimate        | 0           | 108;110    | 113  |
| DECREASE-IV | Distribution estimate | 0           | 1054       | 1067 |
|            | Point estimate        | 0           | 718        | 1067 |

>>>>

load('../data/result_almost_iv_uncertain')
load('../data/result_almost_iv_certain')

# load('data/result_almost_i_uncertain')
# load('data/result_almost_i_certain')
# 
# load('data/result_almost_iv_uncertain')
# load('data/result_almost_iv_certain')

res_i_uncertain <- result_almost_i_uncertain / iterations
res_i_certain <- result_almost_i_certain / iterations

res_iv_uncertain <- result_almost_iv_uncertain / iterations
res_iv_certain <- result_almost_iv_certain / iterations

res_i_uncertain_lb <- NULL
res_i_uncertain_ub <- NULL
res_i_certain_lb <- NULL
res_i_certain_ub <- NULL

res_iv_uncertain_lb <- NULL
res_iv_uncertain_ub <- NULL
res_iv_certain_lb <- NULL
res_iv_certain_ub <- NULL

j <- 1
for (i in seq(0, 1, .01))
{
  lb <- .5 - (i / 2)
  ub <- .5 + (i / 2)

  res_i_uncertain_lb[j] <- which(abs(res_i_uncertain - lb) == min(abs(res_i_uncertain - lb)))[1]
  res_i_uncertain_ub[j] <- which(abs(res_i_uncertain - ub) == min(abs(res_i_uncertain - ub)))[1]

  res_i_certain_lb[j] <- which(abs(res_i_certain - lb) == min(abs(res_i_certain - lb)))[1]
  res_i_certain_ub[j] <- which(abs(res_i_certain - ub) == min(abs(res_i_certain - ub)))[1]

  res_iv_uncertain_lb[j] <- which(abs(res_iv_uncertain - lb) == min(abs(res_iv_uncertain - lb)))[1]
  res_iv_uncertain_ub[j] <- which(abs(res_iv_uncertain - ub) == min(abs(res_iv_uncertain - ub)))[1]

  res_iv_certain_lb[j] <- which(abs(res_iv_certain - lb) == min(abs(res_iv_certain - lb)))[1]
  res_iv_certain_ub[j] <- which(abs(res_iv_certain - ub) == min(abs(res_iv_certain - ub)))[1]

  j <- j + 1
}

# Manually correct some errors in the bound seeking from the loop above
# errors arise from Monte Carlo error:
# .022 .021 .023 <-- selects .021, but should select 0
# considering that running >10000 takes ages and does not guarantee
# it will fix the problem, I do it like this
res_i_uncertain_lb <- ifelse(res_i_uncertain_lb == 4, 0, res_i_uncertain_lb)
res_i_certain_lb <- ifelse(res_i_certain_lb == 1, 0, res_i_certain_lb)
res_iv_uncertain_lb <- ifelse(res_iv_uncertain_lb == 8, 0, res_iv_uncertain_lb)
res_iv_certain_lb[98:101] <- 0
res_iv_certain_ub[98:101] <- 1067

par(mar = c(2.5, 5, 0.5, 0.5),
    mfrow = c(2, 2))
plot(res_i_uncertain,
     xlab = '',
     ylab = 'Proportion',
     ylim = 0:1,
     type = 'l',
     lty = 1)
lines(res_i_certain, pch = 2, type = 'l', lty = 2)
abline(h = c(.025, .975), lty = 3)

legend(x = 0, y = .9, bty = 'n', lty = c(1, 2), legend = c("Distribution estimate", "Point estimate"))

plot(x = NA, y = NA,
     xlim = c(0,1), ylim = c(0, length(res_i_certain)),
     xlab = "Confidence in %", ylab = "Data points fabricated")

lines(x = seq(0, 1, .01), y = res_i_uncertain_lb)
lines(x = seq(0, 1, .01), y = res_i_uncertain_ub)
lines(x = seq(0, 1, .01), y = res_i_certain_lb, lty = 2, pch = 2, type = 'l')
lines(x = seq(0, 1, .01), y = res_i_certain_ub, lty = 2, pch = 2, type = 'l')
abline(v = .95, lty = 3)

# clip(x1 = 0, x2 = length(res_i_uncertain), y1 = 0.025, y2 = .975)
# abline(v = which(abs(res_i_uncertain - .975) == min(abs(res_i_uncertain - .975))), lty = 1)
# abline(v = which(abs(res_i_certain - .975) == min(abs(res_i_certain - .975))), lty = 2)

@@

plot(x = NA, y = NA,
     xlim = c(0,1), ylim = c(0, length(res_iv_certain)),
     xlab = "Confidence in %", ylab = "Data points fabricated")

lines(x = seq(0, 1, .01), y = res_iv_uncertain_lb)
lines(x = seq(0, 1, .01), y = res_iv_uncertain_ub)
lines(x = seq(0, 1, .01), y = res_iv_certain_lb, lty = 2, pch = 2, type = 'l')
lines(x = seq(0, 1, .01), y = res_iv_certain_ub, lty = 2, pch = 2, type = 'l')
abline(v = .95, lty = 3)
```
*Figure `r fig <- fig + 1; fig`*.
